\section*{Bibliography}

\begin{thebibliography}{99}

\bibitem{sui-whitepaper}
Mysten Labs,
``Sui: A Next-Generation Smart Contract Platform with High Throughput, Low Latency, and an Asset-Oriented Programming Model,''
Whitepaper, 2022.

\bibitem{move-language}
S. Blackshear, E. Cheng, D. L. Dill, V. Gao, B. Maurer, T. Nowacki, A. Pott, S. Qadeer, D. Russi, S. Sezer, T. Zakian, and R. Zhou,
``Move: A Language With Programmable Resources,''
2020.

\bibitem{sui-docs}
Mysten Labs,
``Sui Developer Documentation,''
\texttt{https://docs.sui.io/}, 2023.

\bibitem{sentio-docs}
Sentio,
``Sentio Documentation: Sui Indexing,''
\texttt{https://docs.sentio.xyz/}, 2023.

\bibitem{subquery-docs}
SubQuery,
``SubQuery Network: Sui Indexing Documentation,''
\texttt{https://academy.subquery.network/}, 2023.

\bibitem{dune-docs}
Dune Analytics,
``Dune Analytics Documentation,''
\texttt{https://dune.com/docs/}, 2023.

\bibitem{sui-alt-framework}
Mysten Labs,
``Sui Alt Framework,''
GitHub Repository, \texttt{https://github.com/MystenLabs/sui}, 2023.

\bibitem{diesel-docs}
Diesel,
``Diesel: A Safe, Extensible ORM and Query Builder for Rust,''
\texttt{https://diesel.rs/}, 2023.

\bibitem{asynch-rust}
N. Matsakis and A. Turon,
``Rust's Journey to Async/Await,''
Communications of the ACM, 2021.

\bibitem{docker-containerization}
D. Merkel,
``Docker: Lightweight Linux Containers for Consistent Development and Deployment,''
Linux Journal, vol. 2014, no. 239, 2014.

\bibitem{json-performance}
K. Atkin, S. Sheth, and M. Zaniewski,
``JSON vs. XML: Performance comparison for real-time applications,''
Proc. of the International Conference on Artificial Intelligence and Applications, 2021.

\bibitem{blockchain-analytics}
F. Victor and B. Lüders,
``Measuring Ethereum-based ERC20 Token Networks,''
International Conference on Financial Cryptography and Data Security, 2019.

\bibitem{data-sovereignty}
J. Katz, A. J. Menezes, P. C. van Oorschot, and S. A. Vanstone,
``Data Sovereignty in the Blockchain Era,''
Journal of Cryptographic Engineering, 2020.

\bibitem{checkpoint-consensus}
M. Ali, J. Nelson, R. Shea, and M. J. Freedman,
``Checkpoint-based Consensus Protocols: An Empirical Study,''
In Proceedings of the 2021 ACM SIGMOD International Conference on Management of Data, 2021.

\bibitem{dev-experience}
A. E. Gencer, S. Basu, I. Eyal, R. van Renesse, and E. G. Sirer,
``Blockchain Developer Experience: Insights and Recommendations,''
IEEE Software, vol. 37, no. 2, 2020.

\end{thebibliography} 