\section*{Definition of Terms}

\begin{description}
    \item[Blockchain] A distributed ledger technology that maintains a continuously growing list of records, called blocks, which are linked using cryptography.
    
    \item[Checkpoint] In Sui, a checkpoint is a collection of transaction certificates that have been finalized. Checkpoints serve as the unit of finality in Sui's consensus protocol.
    
    \item[dApp] Decentralized Application. A computer application that runs on a distributed computing system rather than a single computer.
    
    \item[Data Indexing] The process of organizing and structuring data from a blockchain to make it more accessible, queryable, and useful for applications.
    
    \item[Data Self-Custody] The principle of maintaining full ownership and control over one's data, rather than relying on third-party services to store or manage it.
    
    \item[DeFi] Decentralized Finance. A blockchain-based form of finance that doesn't rely on central financial intermediaries.
    
    \item[Docker] A platform used to develop, ship, and run applications inside containers, ensuring consistent behavior across different environments.
    
    \item[Full Node] A network node that maintains a complete copy of the blockchain, including all transactions and state transitions.
    
    \item[Indexer] A system that processes blockchain data and organizes it into a database structure that can be efficiently queried.
    
    \item[JSON] JavaScript Object Notation. A lightweight data-interchange format that is easy for humans to read and write and easy for machines to parse and generate.
    
    \item[Move] A programming language designed for writing safe smart contracts, originally developed for the Diem blockchain and adopted by Sui.
    
    \item[Object-Centric Model] Sui's approach to data representation, where the fundamental unit of storage is an object with a unique identifier, rather than an account.
    
    \item[Package] In Sui, a package is a collection of Move modules published together. It's the unit of smart contract deployment.
    
    \item[PostgreSQL] An open-source relational database management system emphasizing extensibility and SQL compliance.
    
    \item[Rust] A multi-paradigm, high-level, general-purpose programming language designed for performance and safety, especially safe concurrency.
    
    \item[SDK] Software Development Kit. A collection of software tools, libraries, and documentation that helps developers create applications for a specific platform.
    
    \item[Smart Contract] Self-executing contracts with the terms directly written into code. They automatically execute transactions when predetermined conditions are met.
    
    \item[Sui] A Layer 1 blockchain designed for high throughput and low latency, featuring an object-centric data model and the Move programming language.
    
    \item[Transaction] An atomic operation that changes the state of the blockchain, such as transferring assets, creating objects, or executing functions on smart contracts.
    
    \item[Transaction Digest] A unique identifier for a transaction, typically represented as a cryptographic hash of the transaction data.
\end{description} 